Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2018-05-16 automatica/paper.tex
fixes

Note that a stable closed-loop model is not necessarily a safe model: 
indeed, the state values may leave the safe part of the state space while they converge
to the equilibrium, which is typical in the case of oscillatory and convergent dynamics. 
%However, a safe system will always be stable.  
In~this work, the safety property is expressed as the formula:
%
\begin{equation}
\label{eq:safetyliteral}
\phi_\mathit{safety} := \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
\end{equation}
%
%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
%
where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$, ranging over the $k$-th time step.  
This means that the states are required to remain within an $n$-dimensional hyper-box at any point in time.

Furthermore, it is practically relevant to consider constraints $\phi_\mathit{input}$ on the input
signal $u_{k}$ and requirements $\phi_\mathit{init}$ on the initial states $x_0$, 
both of which we be expressed via given bounds as: 
$\phi_\mathit{input} := {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} $, 
and $\phi_\mathit{init} := \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}$. 
For the input signal, these requirements practically mean that the control input saturates in view of physical constraints.

@@

%-------------------------------
 \subsubsection{Abstract Supports for Continuous-Time Dynamics}
 \label{sec:cont_aasup}
%-------------------------------

@@

In this section we discuss two instantiations of CEGIS: 
the first one,
named {\it multi-stage} approach, 
relies on an unfolding of the dynamics up to a completeness threshold; 
the second one is {\it abstraction-based}, 
and it leverages abstraction-refinement \cite{DBLP:conf/cav/ClarkeGJLV00} and acceleration (cf. Sec.~\ref{ssec:aa}) to improve scalability,  
while retaining soundness.

@@

\begin{algorithm}[]
%\scriptsize
\begin{algorithmic}[1]
\Function{$\mathit{safetyCheck}()$}{}
\State assert($ \underline{u}  \leq u \leq \overline{u}$)
 \State set $x_0$ to be a \note{vertex state}, e.g., $[\underline{x_0},\underline{x_0}]$	
\For {($c=0;~c < 2^\mathit{Num\_States};~c\mbox{++}$)}
  %\State assert($ \underline{x_0}  \leq x_0 \leq \overline{x_0}$)
	\For{($i=0;~i< k;~i\mbox{++}$)}
		%\State $u = (\langle I_p,F_p\rangle)((\langle I_c,F_c\rangle)K * (\langle I_c,F_c\rangle) x)$
		\State $u = (plant\_typet)((controller\_typet)K * (controller\_typet) x)$
		\State $x = A * x + B * u$
		\State assert($\underline{x} \leq x \leq \overline{x}$ )
  	\EndFor
  	\State set $x_0$ to be a new vertex state
  	\EndFor
  %\State Return $K$
\EndFunction
\end{algorithmic}
\caption{Safety check\label{alg:safetycheck}}
\end{algorithm}

\item The first {\sc verify} stage, {\sc safety}, shown in Alg.~\ref{alg:safetycheck}, checks that the candidate
solution $K$, which we synthesized to be safe for at least one initial
state, is safe for \emph{all} possible initial states, i.e., does not reach
an unsafe state within $k$ steps.  After unfolding the transition system corresponding
to the previously synthesized controller $k$ steps, we check that the safety
specification holds for any initial state.

@@

\item The third {\sc verify} stage, {\sc complete}, checks that the current
$k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
completeness threshold $\overline{k}$ for the current candidate controller $K$ and
check that $k{\geq}\overline{k}$.  This is done by computing the number of time steps
required for the states to have completed a 360\textdegree circle, as illustrated in Fig.~\ref{fig:ct}. 
\note{This is only for spiralling dynamics - more generally, we need to clarify how the CT is computed. }

>>>>

Note that a stable closed-loop model is not necessarily a safe model: 
indeed, the state values may leave the safe part of the state space while they converge
to the equilibrium, which is typical in the case of oscillatory and convergent dynamics. 
%However, a safe system will always be stable.  
In~this work, the safety property is expressed as the formula:
%
\begin{equation}
\label{eq:safetyliteral}
\phi_\mathit{safety} := \forall k\ge 0,\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
\end{equation}
%
%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
%
where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$, ranging over the $k$-th time step.  
This means that the states are required to remain within an $n$-dimensional hyper-box at any point in time.

Furthermore, it is practically relevant to consider constraints $\phi_\mathit{input}$ on the input
signal $u_{k}$ and requirements $\phi_\mathit{init}$ on the initial states $x_0$, 
both of which we be expressed via given bounds as: 
$\phi_\mathit{input} := {\forall k\ge 0, \underline{u} \leq u_{k} \leq \overline{u}} $, 
and $\phi_\mathit{init} := \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}$. 
For the input signal, these requirements practically mean that the control input saturates in view of physical constraints.

@@

%-------------------------------
 \subsubsection{Abstract supports for continuous-time models}
 \label{sec:cont_aasup}
%-------------------------------

@@

In this section we discuss two instantiations of CEGIS: 
the first one,
named {\it multi-stage} approach, 
relies on an unfolding of the dynamics up to a completeness threshold; 
the second one is {\it abstraction-based}, 
and it leverages abstraction-refinement \cite{DBLP:conf/cav/ClarkeGJLV00} and abstract acceleration (cf. Sec.~\ref{ssec:aa}) to improve scalability,  
while retaining soundness.

@@

\begin{algorithm}[]
%\scriptsize
\begin{algorithmic}[1]
\Function{$\mathit{safetyCheck}()$}{}
\State assert($ \underline{u}  \leq u \leq \overline{u}$)
 \State set $x_0$ to be a \note{vertex state[?]}, e.g., $[\underline{x_0},\underline{x_0}]$	
\For {($c=0;~c < 2^\mathit{Num\_States};~c\mbox{++}$) }
  %\State assert($ \underline{x_0}  \leq x_0 \leq \overline{x_0}$)
	\For{($i=0;~i< k;~i\mbox{++}$)}
		%\State $u = (\langle I_p,F_p\rangle)((\langle I_c,F_c\rangle)K * (\langle I_c,F_c\rangle) x)$
		\State $u = (plant\_typet)((controller\_typet)K * (controller\_typet) x)$
		\State $x = A * x + B * u$
		\State assert($\underline{x} \leq x \leq \overline{x}$ )
  	\EndFor
  	\State set $x_0$ to be a new \note{vertex state}
  	\EndFor
  %\State Return $K$
\EndFunction
\end{algorithmic}
\caption{Safety check\label{alg:safetycheck}}
\end{algorithm}

\item The first {\sc verify} stage, {\sc safety}, shown in Alg.~\ref{alg:safetycheck} \note{Num\_States = ?, plant\_typet = ? controller_typet =?}, checks that the candidate
solution $K$, which we synthesized to be safe for at least one initial
state, is safe for \emph{all} possible initial states, i.e., does not reach
an unsafe state within $k$ steps.  After unfolding the transition system corresponding
to the previously synthesized controller $k$ steps, we check that the safety
specification holds for any initial state.

@@

\item The third {\sc verify} stage, {\sc complete}, checks that the current
$k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
completeness threshold $\overline{k}$ for the current candidate controller $K$ and
check that $k{\geq}\overline{k}$.  This is done by computing the number of time steps
required for the states to have completed a 360\textdegree circle, as illustrated in Fig.~\ref{fig:ct}. 
\note{This is only for spiralling dynamics - more generally, we need to clarify how the CT is computed. Shall we add the CAV17 proof?}
